---
title: "SRT411A0.Rmd"
author: "Yakov Kadashevitch"
date: "February 19, 2018"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
Github Username: Ykadashevitch
---

### Assignment Description
The following assignment is a demonstration using the text from https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf
to read, understand, and demonstrate different actions and results using
the power of R.


### Sources Used
The following sources were used in the process of creating this document:
http://rmarkdown.rstudio.com/
http://nicercode.github.io/guides/reports/
http://kbroman.org/knitr_knutshell/pages/markdown.html
https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf


Used to change the working directory.
```{r}
setwd("/home/yak/Desktop")
```


### Todo 1
Compute the difference between 2014 and the
year  you  started  at  this  university  and  divide
this by the difference between 2014 and the year
you  were  born.   Multiply  this  with  100  to  get
the  percentage  of  your  life  you  have  spent  at
this university.  Use brackets if you need them.

```{r}
((2015-2014)/(2014-1995))*100
```
### Todo 2
Repeat  the  previous  ToDo,  but  with  several
steps  in  between.   You  can  give  the  variables
any name you want, but the name has to start
with a letter.

```{r}
A= ((2015-2014)/(2014-1995))*100
A
```
### Todo 3
Compute the sum of 4, 5, 8 and 11 by first com-
bining  them  into  a  vector  and  then  using  the
function sum.

```{r}
sum(4,5,8,11)
```
### Todo 4
Plot 100 normal random numbers.

```{r}
plot(rnorm(100))
```



### Todo 5
Find help for the sqrt function.

```{r}
help(sqrt)
```
### Todo 6
Make a file called firstscript.R containing R- code  that  generates  100  random  numbers  and plots them, and run this script several times.

```{r}
source("firstscript.R")
```


### Todo 7
Put  the  numbers  31  to  60  in  a  vector  named
P and in a matrix with 6 rows and 5 columns
named Q. Tip:  use the function seq.  Look at
the different ways scalars, vectors and matrices
are denoted in the workspace window.

```{r}
P= seq(from=31, to=60, by=1)
Q= matrix(P,ncol= 5, nrow= 6)
P
Q
```


### Todo 8
Make  a  script  file  which  constructs  three  ran-
dom  normal  vectors  of  length  100.   Call  these
vectors x1, x2 and x3. Make a data frame called t
with three columns (called a,b and c) containing  respectively
x1, x1+x2 and x1+x2+x3.
Call the following functions for this data frame: plot(t)
and sd(t). Can you understand the results?  Rerun this script a few times.

```{r}
```

```{r}
x1=rnorm(100)
x2=rnorm(100)
x3=rnorm(100)
t=data.frame(a=x1,b=x1+x2,c=x1+x2+x3)
plot(t)
```


### Todo 9
Add these lines to the script file of the previous
section.  Try to find out, either by experiment-
ing or by using the help, what the meaning is of
rgb, the last argument of rgb, lwd, pch, cex.

```{r}
```

```{r}
plot(t$a, type="l", ylim=range(t), lwd=3, col=rgb(1,0,0,0.3))
lines (t$b, type="s", lwd=2, col=rgb (0.3,0.4,0.3,0.9))
points (t$c, pch=20, cex=4, col=rgb(0,0,1,0.3))
```

### Todo10
Make  a  file  called tst1.txt
in  Notepad  from the  example  in  Figure  4  and  store  it  in  your
working directory.  Write a script to read it, to multiply the column called g
by 5 and to store it as tst2.txt.

```{r}
d = data.frame (g = c (3,4,5), y = c(12,43,54))
write.table(d, file="tst1.txt", row.names=FALSE)
d2 = read.table(file="tst1.txt", header=TRUE)
d2$g*5
```

### Todo11
Compute the mean of the square root of a vec-
tor  of  100  random  numbers.   What  happens?
Make a vector from 1 to 100.  Make a for-loop
which runs through the whole vector.  Multiply
the elements which are smaller than 5 and larger
than 90 with 10 and the other elements with 0.1.
```{r}
sqrt (mean(rnorm(100)))
```

### Todo12
Make  a  graph  with  on  the  x-axis:  today,  Sin-
terklaas  2014  and  your  next  birthday  and  on
the y-axis the number of presents you expect on
each of these days.  Tip:  make two vectors first.

```{r}
x=strptime(c("2018-02-17","2014-12-6", "2018-08-23"), "%Y-%m-%d")
y= c(1,2,3)
plot(x,y)
```

### Todo13
Make a vector from 1 to 100.  Make a for-loop
which runs through the whole vector.  Multiply
the elements which are smaller than 5 and larger
than 90 with 10 and the other elements with 0.1.

```{r}
O=seq(from= 1, to= 100, by= 1)
s = c()
for(i in 1:100)
{
  if(O[i]<5)
  {
    s[i]=O[i]*10;
  }
  else if(O[i]>90)
  {
    s[i]=O[i]*10;
  }
  else
  {
    s[i]=O[i]*0.1;
  }
}
s
```

### Todo14
Write  a  function  for  the  previous  ToDo,  so
that   you   can   feed   it   any   vector   you   like
(as  argument). Use  a  for-loop  in  the  function  to  do  the  computation  with  each  ele-
ment.    Use  the  standard  R  function length in   the   specification   of   the   counter.

```{r}
fun1 = function(O){

s = c()
L = length(O)
L
for(i in 1:L)
{
  if(O[i]<5)
  {
    s[i]=O[i]*10;
  }
  else if(O[i]>90)
  {
    s[i]=O[i]*10;
  }
  else
  {
    s[i]=O[i]*0.1;
  }
}
s

}

fun1(c(1,2,3,91,92,93,45,46,47))
```


